Investigating Neolithic pottery use from Guijiabao in the Yanyuan Basin in southwest China using organic residue analysis

### 2023-02-21 analysis/paper/paper.Rmd
corrected the IS

```{r chromatograms-plots-four, echo=FALSE, fig.cap= "GC-MS chromatograms of fatty acids extracted from four potsherds from Guijiabao abd Gaoshan. Cn:x refers to fatty acid with n carbon atoms and x double bonds. IS indicates internal standard used for quantification, including FA C21:0 and n-alkane 34"}
knitr::include_graphics(here::here("analysis/figures/chromatograms_four.png"))
```

@@

```{r chromatograms-specific, echo=FALSE, fig.cap= "The MS chromatogram of the Guijiabao potsherd shows the presence of long-chain fatty acids. Cn:x refers to fatty acid with n carbon atoms and x double bonds. IS indicates internal standards used for quantification, including FA C21:0 and n-alkane 34"}
knitr::include_graphics(here::here("analysis/figures/chromatograms_specific.png"))
```

>>>>

```{r chromatograms-plots-four, echo=FALSE, fig.cap= "GC-MS chromatograms of fatty acids extracted from four potsherds from Guijiabao abd Gaoshan. Cn:x refers to fatty acid with n carbon atoms and x double bonds. IS indicates internal standard used for quantification, including FA C21:0 and 5-α Cholestane"}
knitr::include_graphics(here::here("analysis/figures/chromatograms_four.png"))
```

@@

```{r chromatograms-specific, echo=FALSE, fig.cap= "The MS chromatogram of the Guijiabao potsherd shows the presence of long-chain fatty acids. Cn:x refers to fatty acid with n carbon atoms and x double bonds. IS indicates internal standards used for quantification, including FA C21:0 and 5-α Cholestane"}
knitr::include_graphics(here::here("analysis/figures/chromatograms_specific.png"))
```
